% !TEX TS-program = pdflatexmk

\documentclass{letter}

\usepackage{hyperref}

\signature{Will M. Farr}

\address{Birmingham Institute for Gravitational Wave Astronomy\\School
  of Physics and Astronomy\\University of Birmingham\\Birmingham\\B15
  2TT\\United
  Kingdom\\\href{mailto:w.farr@bham.ac.uk}{w.farr@bham.ac.uk}}

\begin{document}

\begin{letter}{Dr.\ Leslie Sage\\968 National Press Building\\529 14th Street NW\\Washington DC 20045-1938\\United States}

\opening{Dear Dr. Sage:}

Thank you very much for notifying us of the provisional acceptance of
our manuscript for Nature Letters, ``Distinguishing Spin-Aligned and
Isotropic Black Hole Populations With Gravitational Waves.''  Since
you have received the last draft, our only edits have been to
re-format the paper appropriately for final submission.  We have 
\begin{itemize}
\item Removed the first footnote, and incorporated the last two
  footnotes into the main text.
\item Removed the URLs from references 32 and 34 (these references are
  complete without them).
\item Removed arXiv numbers from references to published papers.
\item Split the bibliography into two parts, one following the main
  text and one following the ``Methods'' section, with continuous
  numbering.
\item Moved the existing code availability statement to the end of the
  methods section and added a standard ``Data Availability'' statement
  immediately following (both code and data are stored in the same
  public repository on GitHub).
\item Moved figure captions to the end of the main section and methods
  section, and removed figures from the PDF produced by \LaTeX{}.
\item Corrected the references and title for the single table item to
  ``Extended Data Table 1.''
\end{itemize}

I am afraid that on my original submission I must have clicked ``Save
and Exit'' instead of ``Submit,'' so I apologize that this is reaching
you a week late.

\closing{Sincerely,}

\end{letter}

\end{document}
